---
title: "Bootstrapping"
output: github_document
---

```{r setup, include = FALSE}
library(tidyverse)
library(rsample)


knitr::opts_chunk$set(
  fig.width = 6,
  fig.asp = .6,
  out.width = "90%"
)

theme_set(theme_minimal() + theme(legend.position = "bottom"))

options(
  ggplot2.continuous.colour = "viridis",
  ggplot2.continuous.fill = "viridis"
)

scale_colour_discrete = scale_colour_viridis_d
scale_fill_discrete = scale_fill_viridis_d
```

## Simulate data

```{r}
n_samp = 250

sim_df_const = 
  tibble(
    x = rnorm(n_samp, 1, 1),
    error = rnorm(n_samp, 0, 1),
    y = 2 + 3 * x + error
  )

sim_df_nonconst = sim_df_const %>% 
  mutate(
  error = error * .75 * x,
  y = 2 + 3 * x + error
)
```

Plot the datasets

```{r}
sim_df = 
  bind_rows(const = sim_df_const, nonconst = sim_df_nonconst, .id = "data_source") 

sim_df %>% 
  ggplot(aes(x = x, y = y)) + 
  geom_point(alpha = .5) +
  stat_smooth(method = "lm") +
  facet_grid(~data_source) 
```

```{r}
lm(y ~ x, data = sim_df_const) %>% 
  broom::tidy() %>% 
  knitr::kable(digits = 3)

lm(y ~ x, data = sim_df_nonconst) %>% 
  broom::tidy() %>% 
  knitr::kable(digits = 3) ## lm gives results given assumptions are true, 但sim_df_nonconst并不是normal distribution， 所以即便是standard error很小，结果也是不准确的，解决这个问题的办法就是用bootstrap
```


## draw one bootstrap sample

 one bootstrap 相当于取跟raw data相同sample size的samples， 但是每次只取一个，每次都放回，所以有些sample会被反复取
create bootstrap function
```{r}
boot_sample = function(df) {
  sample_frac(df, replace = TRUE)
} 

# replace = TRUE,makes sample size fixed, 每次取必放回
```


check if this works...

```{r}
boot_sample(sim_df_nonconst) %>% 
  ggplot(aes(x = x, y = y)) + 
  geom_point(alpha = .5) +
  stat_smooth(method = "lm")
```

## Many samples and analysis

```{r}
boot_straps = 
  data_frame(
    strap_number = 1:1000,
    strap_sample = rerun(1000, boot_sample(sim_df_nonconst))
  )

boot_straps ###相当于做1000次bootstrap，每次都取跟raw data samples size一致的sample数量

boot_straps %>% pull(strap_sample) %>% .[[1]]
```


```{r}
boot_straps %>% 
  filter(strap_number %in% 1:2) %>% 
  mutate(strap_sample = map(strap_sample, ~arrange(.x, x))) %>% 
  pull(strap_sample)

boot_straps %>% 
  filter(strap_number %in% 1:3) %>% 
  unnest(strap_sample) %>% 
  ggplot(aes(x = x, y = y)) + 
  geom_point(alpha = .5) +
  stat_smooth(method = "lm", se = FALSE) +
  facet_grid(~strap_number) 
```



Can I run my analysis on these.. ? yes

```{r}
boot_results = 
  boot_straps %>% 
  mutate(
    models = map(.x = strap_sample, ~lm(y ~ x, data = .x)),
    results = map(models, broom::tidy)
  ) %>% 
  select(strap_number, results) %>% 
  unnest(results)
  
boot_results
```

What do we have now?

```{r}
boot_results %>% 
  group_by(term) %>% 
  summarize(
    mean_est = mean(estimate),
    boot_se = sd(estimate)) %>% 
  knitr::kable(digits = 3)

## bootstrap help us get the actual standard error under repeated sampling not assuming constant variance
```

Look at the distribution

```{r}
boot_results %>% 
  filter(term == "x") %>% 
  ggplot(aes(x = estimate)) +
  geom_density()
```

construct bootstrap CI

```{r}
boot_results %>% 
  group_by(term) %>% 
  summarize(
    ci_lower = quantile(estimate, 0.025), 
    ci_upper = quantile(estimate, 0.975))
```


```{r}
boot_straps %>% 
  unnest(strap_sample) %>% 
  ggplot(aes(x = x, y = y)) + 
  geom_line(aes(group = strap_number), stat = "smooth", method = "lm", se = FALSE, alpha = .1, color = "blue") +
  geom_point(data = sim_df_nonconst, alpha = .5)
```


## Boot strap using modelr

can we simplify anything...?
 yes
```{r}
sim_df_nonconst %>% 
  bootstraps(1000) %>% 
  mutate(
    models = map(.x = splits, ~lm(y ~ x, data = .x)),
    results = map(models, broom::tidy)
  ) %>% 
  select(id, results) %>% 
  unnest(results) %>% 
  group_by(term) %>% 
  summarize(
    mean_est = mean(estimate),
    boot_se = sd(estimate)) %>% 
  knitr::kable(digits = 3)
```
 
 


